A word-sense representation for documents based on information value and word sense disambiguation

### 2014-03-19 paper/top_senses_definitions.tex
some improvements on tables
fix top 5 senses table!

%\begin{tabular}{ p{2cm} p{5cm} }
\begin{tabular*}{\hsize}{@{\extracolsep{\fill}}p{2.5cm} p{5.3cm}}
    \toprule
    Synset & Gloss  \cr
    \hline
\midrule  \multicolumn{2}{c}{Lenin: The Agrarian Programme}  \\  \midrule
rent.n.01 & a payment or series of payments made by the lessee to an owner for use of some property, facility, equipment, or service \\
land.n.04 & the solid part of the earth's surface \\
peasant.n.01 & a country person \\
capital.n.01 & assets available for use in the production of further assets \\
revolution.n.01 & a drastic and far-reaching change in ways of thinking and behaving \\
\midrule  \multicolumn{2}{c}{The State and Revolution} \\  \midrule
marx.n.03 & United States comedian; one of four brothers who made motion pictures together (1891-1961) \\
revolution.n.01 & a drastic and far-reaching change in ways of thinking and behaving \\
plant.n.01 & buildings for carrying on industrial labor \\
engels.n.01 & socialist who wrote the Communist Manifesto with Karl Marx in 1848 (1820-1895) \\
club.n.02 & a formal association of people with similar interests \\
\midrule  \multicolumn{2}{c}{Lenin: MATERIALISM and EMPIRIO-CRITICISM} \\  \midrule
physics.n.01 & the science of matter and energy and their interactions \\
sociable.n.01 & a party of people assembled to promote sociability and communal activity \\
space.n.02 & an empty area (usually bounded in some way between things) \\
time.n.05 & the continuum of experience in which events pass from the future through the present to the past \\
berkeley.n.01 & Irish philosopher and Anglican bishop who opposed the materialism of Thomas Hobbes (1685-1753) \\
\midrule  \multicolumn{2}{c}{Lenin: Imperialism, the Highest Stage of Capitalism} \\  \midrule
enterprise.n.02 & an organization created for business ventures \\
depository\_financial\_institution.n.01 & a financial institution that accepts deposits and channels the money into lending activities \\
imperialism.n.01 & a policy of extending your rule over foreign countries \\
universe.n.01 & everything that exists anywhere \\
million.n.01 & the number that is represented as a one followed by 6 zeros \\
\midrule  \multicolumn{2}{c}{Lenin: What Is To Be Done?} \\  \midrule
local\_anesthetic.n.01 & anesthetic that numbs a particular area of the body \\
organization.n.01 & a group of people who work together \\
marriage.n.01 & the state of being a married couple voluntarily joined for life (or until divorce) \\
criticism.n.03 & a written evaluation of a work of literature \\
revolutionist.n.01 & a radical supporter of political or social revolution \\
    \bottomrule
\end{tabular*}

>>>>

\begin{table*}[ht]
\caption{Top 5 Senses with Closest Handpicked Synset}
\centering
\begin{tabular}{ p{2.5cm} p{9cm} p{2.5cm}}
    \toprule
    Synset & Gloss  & Handpicked \cr
    \hline
    \midrule  \multicolumn{3}{c}{The State and Revolution} \\  \midrule
    revolution.n.01 & a drastic and far-reaching change in ways of thinking and behaving & revolution.n.01\\
    imperialism.n.02 & a political orientation that advocates imperial interests & communism.n.02\\
    proletarian.n.01 & a member of the working class (not necessarily employed) & peer.n.01\\
    war.n.01 & the waging of armed conflict against an enemy & experience.n.03\\
    practice.n.03 & translating an idea into action & experience.n.03\\
    \midrule  \multicolumn{3}{c}{Lenin: Imperialism, the Highest Stage of Capitalism} \\  \midrule
    proletarian.n.01 & a member of the working class (not necessarily employed) & capitalist.n.02\\
    hair.n.01 & a covering for the body (or parts of it) consisting of a dense growth of threadlike structures (as on the human head); helps to prevent heat loss & universe.n.01\\
    money.n.01 & the most common medium of exchange; functions as legal tender & penny.n.02\\
    practice.n.03 & translating an idea into action & monopoly.n.01\\
    toilet.n.04 & the act of dressing and preparing yourself & monopoly.n.01\\
    \midrule  \multicolumn{3}{c}{Lenin: MATERIALISM and EMPIRIO-CRITICISM} \\  \midrule
    revolution.n.01 & a drastic and far-reaching change in ways of thinking and behaving & experience.n.03\\
    proletarian.n.01 & a member of the working class (not necessarily employed) & helmholtz.n.01\\
    philosophy.n.02 & the rational investigation of questions about existence and knowledge and ethics & physics.n.01\\
    war.n.01 & the waging of armed conflict against an enemy & experience.n.03\\
    strategy.n.02 & the branch of military science dealing with military command and the planning and conduct of a war & physics.n.01\\
    \midrule  \multicolumn{3}{c}{Lenin: What Is To Be Done?} \\  \midrule
    imperialism.n.02 & a political orientation that advocates imperial interests & political\_orientation.n.01\\
    proletarian.n.01 & a member of the working class (not necessarily employed) & worker.n.01\\
    practice.n.03 & translating an idea into action & motion.n.03\\
    money.n.01 & the most common medium of exchange; functions as legal tender & mass.n.01\\
    war.n.01 & the waging of armed conflict against an enemy & motion.n.03\\

    \midrule  \multicolumn{3}{c}{Lenin: The Agrarian Programme of Social-Democracy in the First Russian Revolution, 1905-1907} \\  \midrule
    revolution.n.01 & a drastic and far-reaching change in ways of thinking and behaving & revolution.n.01\\
    capitalism.n.01 & an economic system based on private ownership of capital & capitalism.n.01\\
    proletarian.n.01 & a member of the working class (not necessarily employed) & peasant.n.01\\
    war.n.01 & the waging of armed conflict against an enemy & nationalization.n.03\\
    practice.n.03 & translating an idea into action & nationalization.n.03\\

    \bottomrule
\end{tabular}
\end{table*}
